%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\summarySection}{
  \small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Venkata Midhun Mareedu} \\[4pt]
    \small D.No: 3-24, Patwarigudem, Dammapeta, Bhadradri Kothagudem, Telangana, Pincode: 507306, India, +916300399969
    \small \href{mailto:midhunmareedu@gmail.com}{\underline{midhunmareedu@gmail.com}} $|$ 
    \href{http://midhunmareedu.vercel.app}{\underline{midhunmareedu.vercel.app}} $|$
    \href{http://github.com/venkatmidhunmareedu}{\underline{github.com/venkatmidhunmareedu}} \\[3pt]
\end{center}

% %-----------PROFESSIONAL SUMMARY-----------
% \section{Professional Summary}
%   \vspace{1pt}
%   \summarySection{Aspiring AI Engineer and Full Stack Developer focused on building production-grade \textbf{Generative AI} applications with \textbf{Large Language Models (LLMs)}, \textbf{RAG (Retrieval-Augmented Generation)}, and prompt engineering. Experienced in integrating AI systems into scalable web products using \textbf{Next.js}, \textbf{FastAPI}, \textbf{Vercel's AI SDK}, and modern AI toolchains. Strong track record of translating machine learning capabilities into reliable user-facing features for real-world, data-driven workflows.}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {JNTU-GV}{Vijayanagaram, Andhra Pradesh}
      {Bachelor of Technology, Computer Science \& Engineering}{Jan. 2021 -- April 2024}
  \resumeSubHeadingListEnd


  
%
%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, Go, C} \\
     \textbf{AI/ML}{: Generative AI, Large Language Models (LLMs), RAG, Prompt Engineering, Context Engineering, LangChain.js, Vercel AI SDK, Ollama, Vector Databases, MCP (Servers \& Clients)} \\
     \textbf{Frameworks \& Libraries}{: React.js, Next.js, Electron.js, Node.js, Express.js, FastAPI} \\
     \textbf{Developer Tools}{: Turborepo, Vite, Docker, k9s, Git} \\
     \textbf{UI Frameworks \& Styling}{: Tailwind CSS, shadcn UI, Framer Motion} \\
     \textbf{Databases}{: MySQL, PostgreSQL, MongoDB, VectorDB (ChromaDB, LanceDB)}
    }}
 \end{itemize}


%-------------------------------------------


%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SDE-I}{Aug 2025 -- Present}
      {\href{https://www.deeptaai.com/}{\underline{DeeptaAI}}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Architected scalable AI Chatbot and Form SDKs using Turborepo for cross-platform university integration with reusable LLM orchestration patterns.}
        \resumeItem{Engineered academic infrastructure modules to manage complex program and course hierarchies.}
        \resumeItem{Implemented secure multi-channel payment systems for self-funded and loan-based transactions.}
        \resumeItem{Developed automated post-exam workflows with high-concurrency result processing and re-correction logic, reducing manual operational overhead.}
      \resumeItemListEnd

    \resumeSubheading
      {Associate SDE}{Dec 2024 -- July 2025}
      {\href{https://www.apxor.com/}{\underline{Apxor}}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built a Generative AI chatbot that translated natural language into ClickHouse SQL, enabling automated analytics and data visualization workflows.}
        \resumeItem{Optimized web application performance to 98\% by implementing caching strategies, lighthouse audits, and performance monitoring.}
        \resumeItem{Led frontend development for high-traffic platforms, optimizing performance and user retention for AI-assisted analytics experiences.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Web Developer}{Feb 2024 -- Aug 2024}
      {\href{https://www.incrivelsoft.com/}{\underline{IncrivelSoft, Inc}}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Co-led the frontend team in delivering responsive MERN stack interfaces and high-fidelity UI components.}
        \resumeItem{Integrated complex UI with backend APIs to ensure reliable data flows and seamless end-to-end UX.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\underline{\href{https://github.com/venkatmidhunmareedu/synapse}{Synapse}}} $|$ \emph{Electron.js, React, LanceDB, Ollama, Langchain.js, AI SDK}}{}
          \resumeItemListStart
            \resumeItem{Developed a \textbf{local AI-enhanced PDF viewer} desktop application with LangChain.js and Vercel AI SDK.}
            \resumeItem{Implemented built-in AI features including inline question answering, semantic search, and context-aware page redirection.}
            \resumeItem{Used LanceDB to store embeddings for low-latency retrieval and React PDF Viewer for core document interaction workflows.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Support AI Chatbot} $|$ \emph{React, MongoDB, AI SDK, Go lang}}{}
          \resumeItemListStart
            \resumeItem{Built a \textbf{RAG-driven support chatbot widget + server} (NPM package + script) with configurable system prompts and pluggable tools for enterprise knowledge bases.}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{\underline{\href{https://github.com/venkatmidhunmareedu/overmind}{Overmind}}} $|$ \emph{Skill.md, LaTex}}{}
          \resumeItemListStart
            \resumeItem{Overmind is a LaTeX-based resume workflow for creating a clean base resume and generating role-specific variants quickly. }
            \resumeItem{It is designed for iterative editing in Cursor/VS Code, ATS-oriented tuning, and reproducible PDF output (resume.pdf) from source files in this repository.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
